---
title: "p8105_hw1_ml5363"
author: "Muxin Li"
date: "2025-09-16"
output: github_document
---
## Problem 1
```{r}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

there are variables: `r names(early_january_weather)` in the dataset, the size of dataset is `r nrow(early_january_weather) * ncol(early_january_weather)`, the mean temperature is `r mean(pull(early_january_weather,temp))`

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_plot.pdf")
```

The scatterplot shows a clear diurnal pattern in temperature over time: temperatures tend to rise during daytime and drop overnight. Coloring by humid  shows that warmer periods generally coincide with lower humidity, while cooler periods tend to have higher humidity.

## Problem 2
```{r}

example_df = tibble(
  random_sample= rnorm(10),
  logical_vector= c(random_sample>0),
  character_vector= c(sample(letters,10)),
  score_factor= factor(sample(c("Low","Medium","High"), 10, replace=TRUE))
)
example_df
```

the mean of random sample is `r mean(pull(example_df,random_sample))`
the mean of logical vector is `r mean(pull(example_df,logical_vector))`
the mean of character vector is `r mean(pull(example_df,character_vector))`
the mean of score factor is `r mean(pull(example_df,score_factor))`